--- 
title: "Process Mining 101"
author: "Phil Walker"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This book aims to document what I've been learning about process mining/ process mapping and then be a place to share with others"
---

# Welcome

This book aims to document what I've been learning about process mining/ process mapping and then be a place to share with others

There are different tools available, but the one we will largely focus on exists within the R ecosystem. It is called bupaR (Business Process Analysis in R) and the documentation site for that package and the rest of the '-verse' can be found at [http://bupar.net/]

```{r eval=FALSE}
install.packages("bupaR")

```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
